---
title: "R Notebook"
output:
  html_notebook: default
  html_document: default
---

###Setup Chunk
```{r setup}
message("Hi, I'm setting things up here")
Sys.sleep(1)
```

###Install Package
Uncomment to run
```{r}
#install.packages("shiny")
# install.packages("dygraphs")
# install.packages("rbokeh")
# install.packages("magrittr")
# install.packages("highcharter")
# install.packages("visNetwork")
# install.packages("networkD3")
# install.packages("d3heatmap")
# install.packages("DT")
# install.packages("threejs")
# install.packages("rgl")
# install.packages("rglwidget")
# install.packages("htmltools")
# install.packages("DiagrammeR")
# install.packages("metricsgraphics")
# install.packages("leaflet")
# install.packages("ggplot2")
# install.packages("lattice")
# install.packages("plotly")
# install.packages("jpeg")
```


###GoogleVis
```{r}
#library(googleVis)
#Bar <- gvisBarChart(head(mtcars))
#plot(Bar)
```

###Is working directory the same?
```{r}
getwd()
```

###Plot and Order Tests
```{r}
#Sys.sleep(10)
plot(cars)
1+1
plot(iris)
pi
```



###Shiny in a Chunk:
What's supposed to happen? Shouldn't explode
```{r}
#library(rmdexamples)
#kmeans_cluster(iris)
```

###rnorm
```{r}
rnorm(5)
```

###Python Chunk
```{python}
x = 'hello, python world!'
print(x)
print(x.split(' '))
```

###Rcpp chunk
```{Rcpp}

```

###Warnings and Messages
```{r, message=FALSE, warning=FALSE}
message("hi")
Sys.sleep(1)
message("hi2")
Sys.sleep(1)
warning()
```

###Stop Test
```{r}
#stop(foo)
```



<!-- START HTML WIDGETS --> 
#HTML WIDGETS

###Leaflet
http://geog.uoregon.edu/bartlein/old_courses/geog414s05/data/orstationc.csv
```{r}
# #library(leaflet)
# pal <- colorQuantile("YlOrRd", NULL, n = 8)
# leaflet(orstationc) %>% 
#   addTiles() %>%
#   addCircleMarkers(color = ~pal(tann))
```


###dygraphs
```{r fig.width=3, fig.height=3}
library(dygraphs)
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))
Sys.sleep(1)
```

###plotly
```{r hello}
library(plotly)
p <- ggplot(data = diamonds, aes(x = cut, fill = clarity)) +
            geom_bar(position = "dodge")
ggplotly(p)
```

###rbokeh
```{r}
library(rbokeh)
figure(width = NULL, height = NULL) %>%
  ly_points(Sepal.Length, Sepal.Width, data = iris,
    color = Species, glyph = Species,
    hover = list(Sepal.Length, Sepal.Width))
```

###Highcharter
```{r}
library(magrittr)
library(highcharter)
highchart() %>% 
  hc_title(text = "Scatter chart with size and color") %>% 
  hc_add_serie_scatter(mtcars$wt, mtcars$mpg,
                       mtcars$drat, mtcars$hp)
```

###visNetwork
```{r}
library(visNetwork)
nodes <- data.frame(id = 1:6, title = paste("node", 1:6), 
                    shape = c("dot", "square"),
                    size = 10:15, color = c("blue", "red"))
edges <- data.frame(from = 1:5, to = c(5, 4, 6, 3, 3))
visNetwork(nodes, edges) %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)
```

###networkD3
```{r}
library(networkD3)
data(MisLinks, MisNodes)
forceNetwork(Links = MisLinks, Nodes = MisNodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             Group = "group", opacity = 0.4)
```

###d3heatmap
```{r}
library(d3heatmap)
d3heatmap(mtcars, scale="column", colors="Blues")
```

###DataTables
```{r}
library(DT)
datatable(iris)
```

###threejs
```{r}
library(threejs)
z <- seq(-10, 10, 0.01)
x <- cos(z)
y <- sin(z)
scatterplot3js(x,y,z, color=rainbow(length(z)))
```

###rglwidget
```{r}
library(rgl)
library(rglwidget)
library(htmltools)

theta <- seq(0, 6*pi, len=100)
xyz <- cbind(sin(theta), cos(theta), theta)
lineid <- plot3d(xyz, type="l", alpha = 1:0, 
                 lwd = 5, col = "blue")["data"]

browsable(tagList(
  rglwidget(elementId = "example", width = 500, height = 400,
            controllers = "player"),
  playwidget("example", 
             ageControl(births = theta, ages = c(0, 0, 1),
                        objids = lineid, alpha = c(0, 1, 0)),
                        start = 1, stop = 6*pi, step = 0.1, 
                        rate = 6,elementId = "player")
))
```

###DiagrammeR
```{r}
library(DiagrammeR)
grViz("
  digraph {
    layout = twopi
    node [shape = circle]
    A -> {B C D} 
  }")
```

###MetricsGraphics
```{r}
library(metricsgraphics)
mjs_plot(mtcars, x=wt, y=mpg) %>%
  mjs_point(color_accessor=carb, size_accessor=carb) %>%
  mjs_labs(x="Weight of Car", y="Miles per Gallon")
```

###Leaflet2
```{r}
library(leaflet)

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
m  # Print the map
```


<!-- END HTML WIDGETS --> 

###Testing output bounds
```{r stupid for loop, message=TRUE}
for (i in 1:50) {
  message("I'm on :werwerioasdfiojasdf;kojaw;oeijao;idfjnao;dsfinoaiwsefno;aweifnoiawefj;oaweh;oaeihf;oaiwehf;oawiefo;awihefo;ahiwf;ahof;ih;oieofiaw;efin;ofinefiaweifewifawnoef", i)
}

```


###Multiple plots
```{r}
boxplot(1:10~rep(1:2,5))
plot(10:100)
```


### Simple plot
Here is a basic plot using base graphics:

```{r }
plot(x)
```

###Multiple plots
```{r }
boxplot(1:10~rep(1:2,5))
plot(x, y)
```

###ggplot2
```{r}
# ggplot2 examples
library(ggplot2) 
ggplot(diamonds) + geom_bar( aes(carat) )
```



###`lattice` plot
```{r latticeex}
library(lattice)
xyplot(y~x)
```


### Include and Echo output options
Echo=FALSE
```{r echo=FALSE}
head(df)
```
Include=FALSE
```{r include=FALSE}
head(df)
```


### Control figure size
The following is an example of a smaller figure using `fig.width` and `fig.height` options.

```{r , fig.width=3, fig.height=3}
plot(x)
```

```{r smallplot, fig.width=3, fig.height=3}
plot(x)
```

### Images
Download and show
```{r}
download.file("http://i.imgur.com/RVNmr.jpg",'y.jpg', mode = 'wb')
library("jpeg")
jj <- readJPEG("y.jpg",native=TRUE)
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
rasterImage(jj,0,0,1,1)
```


###Chunks with tabs
    ```{r}
      x <- 1:100
      x
    ```
###Chunk without tabs
```{r}
  x <- 1:100
  x
```
